Open-Vocabulary Semantic Parsing\\with both Distributional Statistics and Formal Knowledge

### 2016-03-21 papers/acl2016/paper.tex
Final version of paper submitted to ACL
Former-commit-id: 1b087d5674865b10a45aef3b9160ff87e1c9985d

How should a computer program represent the meaning of a word or a
phrase? Recent work has suggested two vastly different
approaches---distributional vector space models and semantic
parsing---each with its own advantages and disadvantages. On one hand,
distributional models produce a vector representation of the meaning
of each word from a large unlabeled text corpus. These models have
broad coverage, but they also have a shallow semantics centered around
word similarity. On the other hand, semantic parsing translates
natural language into logical queries against a formal knowledge base,
such as Freebase. This approach produces a rich compositional
semantics and furthermore can leverage structured information from the
knowledge base. However, semantic parsers have limited coverage as
they can only represent the meanings of words that can be mapped to
knowledge base predicates. A critical question is \emph{how do we
obtain the benefits of both of these approaches?}

\begin{figure*}[ht]
  \small
  \begin{minipage}{0.18\linewidth}
    \textbf{Input Text}\\Italian architect \blank{}
  \end{minipage}
%
  ~~ $\longrightarrow$ ~~~~~~
%
  \begin{minipage}{0.7\linewidth}
    \textbf{Logical Form}\\
    $\lexicalpredicate{architect}(x)~\land~\lexicalpredicate{architect\_N/N}(\entity{Italy}, x)$
  \end{minipage}

@@

  \begin{minipage}{0.5\linewidth}
    \textbf{Entity models}\\
    \begin{tabular}{@{}lll}
      \entity{Palladio}: & $\phi$: &[.15, -.8, \ldots] \\
      & $\psi$: & \textsc{type:architect} $\rightarrow$ 1 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ 1 \\
      &           & $\cdots$ \\
      \entity{Obama}: & $\phi$: &[.85, .1, \ldots] \\
      & $\psi$: & \textsc{type:politician} $\rightarrow$ 1 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ 0 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \textbf{Entity pair models}\\
    \begin{tabular}{@{}lll}
      \entity{(Italy, Palladio)}: & $\phi$: &[-.8, .2, \ldots] \\
      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 1 \\
      &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
      &           & $\cdots$ \\
      \entity{(Italy, Obama)}: & $\phi$: &[-.2, -.2, \ldots] \\
      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 0 \\
      &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}

  \begin{minipage}{0.5\linewidth}
    \textbf{Output}\\
    \begin{tabular}{@{}ll}
      $\mathrm{prob}(\entity{Palladio})$: & 0.79 \\
      $\mathrm{prob}(\entity{Obama})$: & 0.01 \\
      $\cdots$ \\
    \end{tabular}
  \end{minipage}

@@

Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
introduced a technique for learning semantic parsers with open
predicate vocabularies. Instead of mapping text directly to Freebase
queries, this method parses text to a surface logical form whose
predicates are derived directly from the words in the text (an example
of these logical forms is shown in \figref{overview}). Next, a
distribution over denotations for each predicate is learned using a
matrix factorization approach similar to that of Riedel et
al.~\shortcite{riedel-2013-mf-universal-schema}. This distribution is
concisely represented using a probabilistic database, which also
enables efficient probabilistic execution of logical form queries.

@@

This section presents our approach to open vocabulary semantic
parsing. Our approach follows the same structure as described in
Section \ref{sec:jayant-semparse}: we generate a surface logical form
from a query, then evaluate it against a probabilistic database with
learned predicate instance probabilities. Section \ref{sec:better-lfs}
describes our logical form generation, which improves the analyses of
noun-mediated relations relative to prior work. Sections
\ref{sec:formal-and-distributional} and \ref{sec:feature-generation}
describe our improved predicate models and the corresponding feature
generation process. Finally, Section \ref{sec:better-candidates}
describes an improvement on candidate entity generation for question
answering.

% In \secref{formal-and-distributional} we describe how we modify
% Krishnamurthy and Mitchell's (K\&M's) semantic parser to include
% features from a formal knowledge base.  In \secref{computing-pmi} we
% describe how we select those features for each predicate.  The
% remaining two sections then describe other improvements we made to
% K\&M's semantic parsing model: lexicalizing preposition and
% noun-compound predicates, and using the Freebase graph to select
% candidate entities.

@@

As in K\&M, we generate logical forms from natural language statements
by computing a syntactic CCG parse, then applying a collection of
rules to produce logical forms. However, their logical form analyses
do not model noun-mediated relations well. For example, given the
phrase ``Italian architect Andrea Palladio,'' their system's logical
form would include the relation
$\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea
  Palladio})$. Here, the \lexicalpredicate{N/N} predicate represents a
generic noun modifier relation; however, this relation is too vague
for the predicate model to accurately learn its denotation. A similar
problem occurs with prepositions and possessives, e.g., it is
similarly hard to learn the denotation of the predicate
\lexicalpredicate{of}.

Our system improves the analysis of noun-mediated relations by simply
including the noun in the predicate name. In the architect example
above, our system produces the relation
\lexicalpredicate{architect\_N/N}. It does this by simply
concatenating all intervening noun modifiers between two entity
mentions and including them in the predicate name; for example,
``Illinois attorney general Lisa Madigan'' produces the predicate
\lexicalpredicate{attorney\_general\_N/N}). (While it would be
preferable to use actual dependency relations to determine which words
to add to the predicate, this is not possible because our parser
produces flat analyses of noun phrases where all noun modifiers depend
directly on the head of the noun phrase.) We similarly improve the
analyses of prepositions and possessives to include the head noun. For
example, ``Barack Obama, president of the U.S.'' produces the
predicate instance $\lexicalpredicate{president\_of}(\entity{Barack
  Obama}, \entity{U.S.})$, and ``Rome, Italy's capital'' produces the
predicate \lexicalpredicate{'s\_capital}. This process generates more
specific predicates that we empirically found were easier for the
predicate models to learn.

@@

% TODO: ``query'' features?

We inject information from a knowledge base into our predicate models
by augmenting the learned embeddings with features. The truth
probability of a category instance $c(e)$ or relation instance $r(e_1,
e_2)$ in our model is given by:

@@

In our model, there are now three sets of parameters to be learned:
(1) $\theta$, low-dimensional distributional vectors trained for each
predicate; (2) $\phi$, low-dimensional distributional vectors trained
for each entity and entity pair; and (3) $\omega$, weights associated
with the selected formal SFE features for each predicate.  All of
these parameters are optimized jointly, using the same query ranking
objective used by K\&M.

% For each category and relation, we select a subset of the SFE features in the
% vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
% add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
% predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
% observed features for each entity and entity pair.  The augmented category and
% relation probabilities are as follows:

@@

The predicate-independent feature extraction stage computes the
following feature vectors. For entity pairs, the vector $\psi(e_1,
e_2)$ is a sparse binary vector containing indicator features for all
edge sequences that connect nodes $e_1$ and $e_2$ in the Freebase
graph, up to length 4.  For an entity $e$, we extract two kinds of
features: (1) all edge sequences up to length two that begin at $e$,
and (2) the same sequences paired with the entity at their
endpoint. Features of type (1) capture the kinds of relations that an
entity participates in, e.g., designing architectural structures,
while features of type (2) capture relations to other particular
entities. This second kind of feature is most helpful when the
endpoint entity is a type, such as \entity{architect}, although there
are some other valuable features of this kind. \figref{sfe} shows some
example entity and entity pair features extracted from a subset of the
Freebase graph.

% For each category and relation, we select a subset of the SFE features in the
% vectors $\psi$ to have associated weights $\omega_c$ and $\omega_r$.  We then
% add the weights $\omega_c$ and $\omega_r$ as parameters to be learned for each
% predicate, and we add the feature vectors $\psi(e)$ and $\psi(e_1, e_2)$ as
% observed features for each entity and entity pair.  The augmented category and
% relation probabilities are as follows:
% 
% \begin{align*}
%   P(c(e)) &= \sigma ( \theta_c^T \phi_e + \omega_c^T \psi_c(e)) \\
%   P(r(e_1, e_2)) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} + \omega_r^T \psi_r(e_1, e_2) )
% \end{align*}
% where we have added subscripts on the $\psi$ functions to indicate that each
% predicate selects its own set of features from the SFE feature vector $\psi$.

% The feature vectors returned by SFE have dimensionality in the tens of
% millions.  We do not have near enough data to train that many parameters for
% each of our tens of thousands of predicates, nor do we have enough RAM in our
% machines to keep that many parameters in memory.  It is thus necessary to
% select some small number of informative features for each predicate.  We do
% this using pointwise mutual information (PMI).

The feature selection step uses pointwise mutual information (PMI) to
reduce the number of features considered by the model for each
predicate. The feature vectors generated above have tens of millions
of dimensions, but, for any given surface predicate, only a handful of
these dimensions represent relevant Freebase queries. We select
features by first summing the entity and entity pair feature vectors
seen with each predicate in the training data. For example, the phrase
``Italian architect Andrea Palladio'' is considered a positive
training example for the instantiated predicates
$\formalpredicate{architect}(\entity{Andrea Palladio})$ and
$\formalpredicate{architect\_N/N}(\entity{Italy}, \entity{Andrea
  Palladio})$. We then add the feature vectors for \entity{Andrea
  Palladio} and (\entity{Italy}, \entity{Andrea Palladio}) to the
feature counts for the predicates \formalpredicate{architect} and
\formalpredicate{architect\_N/N}, respectively. Next, for each predicate
$\pi$ and feature $f$, we use these counts to calculate three
probabilities: $p(\pi, f)$, $p(\pi)$ and $p(f)$. (TODO: how did you
calculate these?). The PMI of a predicate/feature pair is then $\log
\frac{p(\pi, f)}{p(\pi)p(f)}$. After removing features with counts
below a threshold, we pick the $k=100$ features with the highest PMI
values for each predicate to use in our model.

% PMI measures the strength of association between two variables $x$ and $y$; it
% is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
% associate predicates with SFE features.  However, our SFE features are for each
% \emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
% SFE features with predicates, we  For each
% predicate $\pi$ and feature $f$, we use these counts to calculate the
% probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.

@@

A key benefit of our predicate models is that they are able to assign
scores to entity pairs that were never seen in the training data. The
purely-distributional model of K\&M has no basis for assigning these
scores and therefore assumes $P(r(e_1,e_2)) = 0$ for unseen entity
pairs $(e_1,e_2)$. This assumption limits the recall of their system
when it is applied to question answering, as these entity pairs will
not have been observed for many correct, but rare entity answers. In
contrast, our predicate models can score any entity pair: the
distributional component of an unseen pair will be zero, but the SFE
component is always applicable. This benefit allows our model to
considerably improve question answering performance on rare entities.

% One final way in which we improved K\&M's semantic parser is in how candidate
% entities are generated during inference.  Because the distributional-only
% predicate models used by K\&M's semantic parser need to learn a vector of
% parameters for each entity pair, they cannot give a non-zero score to any
% entity pair not seen during training time.  When given a query such as
% $\lambda(x).\lexicalpredicate{architect\_N/N}(x, \entity{Andrea
% Palladio})$, K\&M's system only needs to consider the set of entities
% $\entity{x}$ that have been seen at training time with \entity{Andrea
% Palladio}; all other entities will get a score of 0.
% 
% Our predicate models do not have this limitation.  The distributional component
% will still give an unseen entity pair a score of 0, as it is identical to K\&M's
% model, but the formal component of our models simply computes an observed
% feature vector from Freebase for the entity pair.  As long as both entities
% appear in Freebase, our model can compute a feature vector and give a non-zero
% score.

However, this benefit has an associated drawback: given a logical form
query, it is computationally and statistically undesirable to consider
\emph{all} Freebase entities as answers. Scoring millions of entities
is slow, and furthermore makes it more difficult to identify correct
answers (as their frequency in the candidate set
decreases). Therefore, when answering a query, we compute a set of
candidate entities and only score these candidates. Our candidate set
consists of all entities seen with the query entities in the training
set as well as all entities directly connected to the query entities
in Freebase, or connected by a mediator node.\footnote{Mediators in
  Freebase are used to capture relations with more than two arguments,
  such as employment tenure, which has an employer, and employee, a
  start date, and an end date.}

% While this improvement allows us to handle queries over rare entities much
% better than a distributional-only model, it also complicates inference, as we
% cannot just score entity pairs seen at training time.  Optimizing every query's
% score over all of the millions of entities in Freebase is not computationally
% feasible.  To make inference tractable, for a given query we restrict
% candidates to all entities seen with the query entities during training (as
% done by K\&M), as well as all entities directly connected to the query entities
% in Freebase, or connected by a mediator node.\footnote{Mediators in Freebase are
% used to capture relations with more than two arguments, such as employment
% tenure, which has an employer, and employee, a start date, and an end date.}

@@

We evaluate our models of predicate semantics on a fill-in-the-blank
natural language query task.  Each test example is a natural language
phrase containing at least two Freebase entities, one of which is held
out.  The system must propose a ranked list of Freebase entities to
fill in the blank left by the held out entity, and the predicted
entities are then judged manually for correctness.  We compare our
proposed models, which combine distributional and formal elements,
with a purely distributional baseline from prior work.  All of the
data and code used in these experiments is available at [url withheld
for review].

@@

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary},
which consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with
Google's FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training
data, 3 million webpages from this corpus were processed with a CCG
parser to produce logical forms~\cite{krishnamurthy-2014-joint-ccg}.
This produced 2.1m predicate instances involving 142k entity pairs and
184k entities.  After removing infrequently-seen predicates (seen
fewer than 6 times), there were 25k categories and 4.2k relations.
The differences in numbers reported here versus those reported by
Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
due to our improved logical form generation, discussed in
\secref{better-lfs}.

We also used the test set created by Krishnamurthy and Mitchell, which
contains 220 queries generated in the same fashion as the training
data from a separate section of ClueWeb.  However, as they did not
release a development set in with their data, we used this set as a
development set.  For a final evaluation, we generated another,
similar test set from a different held out section of ClueWeb, in the
same fashion as done by Krishnamurthy and Mitchell.  This final test
set contains 307 queries.  We report results on both of these sets
below.

@@

Given a fill-in-the-blank query such as ``Italian architect
\blank{}'', each system produces a ranked list of 100 candidate
entities.  To compare the output of the systems, we follow a pooled
evaluation protocol commonly used in relation extraction and
information
retrieval~\cite{west-2014-kbc-via-qa,riedel-2013-mf-universal-schema}.
We take the top 30 predictions from each system and manually annotate
whether they are correct, and use those annotations to compute the
average precision (AP) and reciprocal rank (RR) of each system on the
query.  Average precision is defined as $\frac{1}{m}\sum^m_{k=1}
\mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where $\mathrm{Prec}(k)$
is the precision at rank $k$, $\mathrm{Correct}(k)$ is an indicator
function for whether the $k$th answer is correct, and $m$ is number of
returned answers (up to 100 in this evaluation).  Reciprocal rank is
computed by first finding the rank $r$ of the first correct prediction
made by a system.  Reciprocal rank is then $\frac{1}{r}$, ranging from
1 (if the first prediction is correct) to 0 (if there is no correct
answer returned).  In the tables below we report \emph{mean} average
precision (MAP) and reciprocal rank (MRR), averaged over all of the
queries in the test set.  We also report a weighted version of MAP,
where the AP of each query is scaled by the number of annotated
correct answers to the query (shown as W-MAP in the tables for space
considerations).

@@

We next show the improvement gained by using the simple candidate
entity generation outlined in \secref{better-candidates}.  By simply
appending the list of connected entities to the end of the rankings
returned by the distributional model, MAP improves by 40\% (see
\tabref{better-candidates}).  The connectedness of an entity pair in
Freebase is very informative, especially for rare entities that are
not seen together during training.

@@

\tabref{dev-results} shows the results of our experiments on the
development set.  As can be seen, the combined model significantly
improves performance over prior work, giving a relative gain in
weighted MAP of 29\%.

@@

\tabref{final-results} shows that these improvements are consistent on
the final test set, as well.  The performance improvement seen by the
combined model is actually larger on this set, with gains on our
metrics ranging from 50\% to 97\%.

@@

Our model tends to outperform the distributional model on queries
containing predicates with exact or partial correlates in
Freebase. For example, our model obtains nearly perfect average
precision on the queries ``French newspaper \blank{}'' and ``Israeli
prime minister \blank{},'' both of which can be exactly expressed in
Freebase. (TODO: do these relations get high weights in the features?)
The model also performs well on queries with partial Freebase
correlates, such as ``Microsoft head honcho \blank{}'', ``The United
States, \blank{}'s closest ally'', and ``Patriots linebacker
\blank{},'' although with somewhat lower average precision. The high
weight features in these cases tend to provide useful hints, even
though there is no direct correlate; for example, the model learns
that ``honchos'' are people, and that they tend to be CEOs and film
producers.

@@

Second, our work is conceptually related to many methods that aim to
learn word embeddings that are informed by some kind of external
knowledge~\cite{faruqui-2015-retrofitting-word-vectors,%
rocktaschel-2015-logical-embeddings,schwartz-2016-symmetric-patterns-w2v,%
yu-2014-w2v-with-semantic-knowledge}.
A key difference between these approaches and ours is that they use
the structured information only to modify distributional
representations, while we include the structured information directly
in our models, training weights for structured information jointly
with distributional representations.

@@

This paper considers the problem of assigning meaning to predicates
(both categories and relations) in natural language using both
distributional information and information from a formal knowledge
base. Our model represents words as a weighted combination of
knowledge base queries plus a distributional component. Both of these
components are jointly trained to correctly predict entity answers to
fill-in-the-blank natural language queries. This combined model
achieved relative gains of over 50\% in mean average precision and
mean reciprocal rank versus prior work.  We also introduced a better
mapping from surface text to logical forms, and a simple method for
using Freebase to find candidate entities during inference.  Taken
together, the methods introduced in this paper improved mean average
precision on our task from .163 to .370, a 127\% relative improvement.

>>>>

How should a computer program represent the meaning of a word or a
phrase? Recent work has suggested two vastly different
approaches---distributional vector space models and semantic
parsing---each with its own advantages and disadvantages. On one hand,
distributional models produce a vector representation of the meaning
of each word from a large unlabeled text corpus. These models have
broad coverage, but only a shallow semantics centered around word
similarity. On the other hand, semantic parsing translates natural
language into logical queries against a formal knowledge base, such as
Freebase. This approach produces a rich compositional semantics and
can leverage structured information from the knowledge base. However,
semantic parsers have limited coverage as they can only represent the
meanings of words that can be mapped to knowledge base predicates. A
critical question is \emph{how do we obtain the benefits of both of
these approaches?}

\begin{figure*}[ht]
  \small
  \begin{minipage}{0.18\linewidth}
    \textbf{Input Text}\\Italian architect \blank{}
  \end{minipage}
%
  ~~ $\longrightarrow$ ~~~~~~
%
  \begin{minipage}{0.7\linewidth}
    \textbf{Logical Form}\\
    $\lambda x.\lexicalpredicate{architect}(x)~\land~\lexicalpredicate{architect\_N/N}(\entity{Italy}, x)$
  \end{minipage}

@@

  \begin{minipage}{0.5\linewidth}
    \textbf{Entity models}\\
    \begin{tabular}{@{}lll}
      \entity{Palladio}: & $\phi$: &[.15, -.8, \ldots] \\
      & $\psi$: & \textsc{type:architect} $\rightarrow$ 1 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ 1 \\
      &           & $\cdots$ \\
      \entity{Obama}: & $\phi$: &[.85, .1, \ldots] \\
      & $\psi$: & \textsc{type:politician} $\rightarrow$ 1 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ 0 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \textbf{Entity pair models}\\
    \begin{tabular}{@{}lll}
      \entity{(Italy, Palladio)}: & $\phi$: &[-.8, .2, \ldots] \\
      & $\psi$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 1 \\
      &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
      &           & $\cdots$ \\
      \entity{(Italy, Obama)}: & $\phi$: &[-.2, -.2, \ldots] \\
      & $\psi$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 0 \\
      &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}

  \begin{minipage}{0.5\linewidth}
    \textbf{Output}\\
    \begin{tabular}{@{}ll}
      $P(\entity{Palladio})$: & 0.79 \\
      $P(\entity{Obama})$: & 0.01 \\
      $\cdots$ \\
    \end{tabular}
  \end{minipage}

@@

Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
introduced a technique for learning semantic parsers with open
predicate vocabularies. Instead of mapping text to Freebase queries,
this method parses text to a surface logical form whose predicates are
derived directly from the words in the text (an example of these
logical forms is shown in \figref{overview}). Next, a distribution
over denotations for each predicate is learned using a matrix
factorization approach similar to that of Riedel et
al.~\shortcite{riedel-2013-mf-universal-schema}. This distribution is
concisely represented using a probabilistic database, which also
enables efficient probabilistic execution of logical form queries.

@@

This section presents our approach to open vocabulary semantic
parsing. Our approach follows the same structure as described in
Section \ref{sec:jayant-semparse}: we generate a surface logical form
from a query, then evaluate it against a probabilistic database with
learned predicate instance probabilities. Section \ref{sec:better-lfs}
describes our logical form generation, which improves the analyses of
noun-mediated relations relative to prior work. Sections
\ref{sec:formal-and-distributional} and \ref{sec:feature-generation}
describe our predicate models and the corresponding feature generation
process. Finally, Section \ref{sec:better-candidates} describes an
improvement on candidate entity generation for question answering.

@@

As done by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, we
generate logical forms from natural language statements by computing a
syntactic CCG parse, then applying a collection of rules to produce
logical forms. However, their logical form analyses do not model
noun-mediated relations well. For example, given the phrase ``Italian
architect Andrea Palladio,'' their system's logical form would include
the relation $\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea
Palladio})$. Here, the \lexicalpredicate{N/N} predicate represents a
generic noun modifier relation; however, this relation is too vague
for the predicate model to accurately learn its denotation. A similar
problem occurs with prepositions and possessives, e.g., it is
similarly hard to learn the denotation of the predicate
\lexicalpredicate{of}.

Our system improves the analysis of noun-mediated relations by simply
including the noun in the predicate name. In the architect example
above, our system produces the relation
\lexicalpredicate{architect\_N/N}. It does this by
concatenating all intervening noun modifiers between two entity
mentions and including them in the predicate name; for example,
``Illinois attorney general Lisa Madigan'' produces the predicate
\lexicalpredicate{attorney\_general\_N/N}).\footnote{While it would be
preferable to use actual dependency relations to determine which words
to add to the predicate, this is not possible because our parser
produces flat analyses of noun phrases where all noun modifiers depend
directly on the head of the noun phrase.} We similarly improve the
analyses of prepositions and possessives to include the head noun. For
example, ``Barack Obama, president of the U.S.'' produces the
predicate instance $\lexicalpredicate{president\_of}(\entity{Barack
  Obama}, \entity{U.S.})$, and ``Rome, Italy's capital'' produces the
predicate \lexicalpredicate{'s\_capital}. This process generates more
specific predicates that we empirically found were easier for the
predicate models to learn.

@@

The key question in the semantic parsing framework we are using is how
to define the predicate models that underlie the probabilistic
database described in \secref{jayant-semparse}.  This is where
previous work used purely distributional models, and where we wish to
include structured information from a knowledge base to improve the
semantics of these predicate models.

We inject information from a knowledge base into our predicate models
by augmenting the learned embeddings with features. In our models, the
truth probability of a category instance $c(e)$ or relation instance
$r(e_1, e_2)$ is given by:

@@

In our model, there are now three sets of parameters to be learned:
(1) $\theta$, low-dimensional distributional vectors trained for each
predicate; (2) $\phi$, low-dimensional distributional vectors trained
for each entity and entity pair; and (3) $\omega$, weights associated
with the selected formal SFE features for each predicate.  All of
these parameters are optimized jointly, using the semantic parsing
framework described in \secref{jayant-semparse}.

@@

The predicate-independent feature extraction stage computes the
following feature vectors. For entity pairs, the vector $\psi(e_1,
e_2)$ is a sparse binary vector containing indicator features for all
edge sequences that connect nodes $e_1$ and $e_2$ in the Freebase
graph, up to length 4.  For an entity $e$, the vector $\psi(e)$
contains two kinds of indicator features: (1) all edge sequences up to
length two that begin at $e$, and (2) the same sequences paired with
the entity at their endpoint. Features of type (1) capture the kinds
of relations that an entity participates in, e.g., designing
architectural structures, while features of type (2) capture relations
to other particular entities. This second kind of feature is most
helpful when the endpoint entity is a type, such as
\entity{architect}, although there are some other valuable features of
this kind. \figref{sfe} shows some example entity and entity pair
features extracted from a subset of the Freebase graph.

The feature selection step uses pointwise mutual information (PMI) to
reduce the number of features considered by the model for each
predicate. The feature vectors generated above have tens of millions
of dimensions, but, for any given surface predicate, only a handful of
these dimensions represent relevant Freebase queries. We select
features by first summing the entity and entity pair feature vectors
seen with each predicate in the training data. For example, the phrase
``Italian architect Andrea Palladio'' is considered a positive
training example for the instantiated predicates
$\formalpredicate{architect}(\entity{Andrea Palladio})$ and
$\formalpredicate{architect\_N/N}(\entity{Italy}, \entity{Andrea
Palladio})$. We then add the feature vectors for \entity{Andrea
Palladio} and (\entity{Italy}, \entity{Andrea Palladio}) to the
feature counts for the predicates \formalpredicate{architect} and
\formalpredicate{architect\_N/N}, respectively. This gives a set of
counts \formalpredicate{count}($\pi$), \formalpredicate{count}($f$),
and \formalpredicate{count}($\pi\land f$), for each predicate $\pi$
and feature $f$.  The features are then ranked by PMI for each feature
by computing $\frac{\formalpredicate{count}(\pi\land
f)}{\formalpredicate{count}(\pi)\formalpredicate{count}(f)}$.  After
removing features with counts below a threshold, we pick the $k=100$
features with the highest PMI values for each predicate to use in our
model.

@@

A key benefit of our predicate models is that they are able to assign
scores to entity pairs that were never seen in the training data. The
purely distributional model of Krishnamurthy and Mitchell has no basis
for assigning these scores and therefore assumes $P(r(e_1,e_2)) = 0$
for unseen entity pairs $(e_1,e_2)$. This assumption limits the recall
of their system when it is applied to question answering, as these
entity pairs will not have been observed for many correct, but rare
entity answers. In contrast, our predicate models can score any entity
pair: the distributional component of an unseen pair will be zero, but
the SFE component is always applicable. This benefit allows our model
to considerably improve question answering performance on rare
entities.

However, this benefit has an associated drawback: given a logical form
query, it is computationally and statistically undesirable to consider
\emph{all} Freebase entities as answers. Scoring millions of entities
is slow, and furthermore makes it more difficult to identify correct
answers (as their relative frequency in the candidate set decreases).
Therefore, when answering a query, we compute a set of candidate
entities and only score these candidates. Our candidate set consists
of all entities seen with the query entities in the training set as
well as all entities directly connected to the query entities in
Freebase, or connected by a mediator node.\footnote{Mediators in
Freebase are used to capture relations with more than two arguments,
such as employment tenure, which has an employer, and employee, a
start date, and an end date.}

@@

We evaluate our open-vocabulary semantic parser on a fill-in-the-blank
natural language query task.  Each test example is a natural language
phrase containing at least two Freebase entities, one of which is held
out.  The system must propose a ranked list of Freebase entities to
fill in the blank left by the held out entity, and the predicted
entities are then judged manually for correctness.  We compare our
proposed models, which combine distributional and formal elements,
with a purely distributional baseline from prior work.  All of the
data and code used in these experiments is available at [url withheld
for review].

@@

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary},
which consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with
Google's FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training
data, 3 million webpages from this corpus were processed with a CCG
parser to produce logical forms~\cite{krishnamurthy-2014-joint-ccg}.
This produced 2.1m predicate instances involving 142k entity pairs and
184k entities.  After removing infrequently-seen predicates (seen
fewer than 6 times), there were 25k categories and 4.2k
relations.\footnote{The differences in numbers reported here versus
those reported by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
due to our improved logical form generation, discussed in
\secref{better-lfs}.}

We also used the test set created by Krishnamurthy and Mitchell, which
contains 220 queries generated in the same fashion as the training
data from a separate section of ClueWeb.  However, as they did not
release a development set with their data, we used this set as a
development set.  For a final evaluation, we generated another,
similar test set from a different held out section of ClueWeb, in the
same fashion as done by Krishnamurthy and Mitchell.  This final test
set contains 307 queries.  We report results on both of these sets
below.

@@

Given a fill-in-the-blank query such as ``Italian architect
\blank{}'', each system produces a ranked list of 100 candidate
entities.  To compare the output of the systems, we follow a pooled
evaluation protocol commonly used in relation extraction and
information
retrieval~\cite{west-2014-kbc-via-qa,riedel-2013-mf-universal-schema}.
We take the top 30 predictions from each system and manually annotate
whether they are correct, and use those annotations to compute the
average precision (AP) and reciprocal rank (RR) of each system on the
query.  Average precision is defined as $\frac{1}{m}\sum^m_{k=1}
\mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where $\mathrm{Prec}(k)$
is the precision at rank $k$, $\mathrm{Correct}(k)$ is an indicator
function for whether the $k$th answer is correct, and $m$ is number of
returned answers (up to 100 in this evaluation).  AP is equivalent to
calculating the area under a precision-recall curve.  Reciprocal rank
is computed by first finding the rank $r$ of the first correct
prediction made by a system.  Reciprocal rank is then $\frac{1}{r}$,
ranging from 1 (if the first prediction is correct) to 0 (if there is
no correct answer returned).  In the tables below we report
\emph{mean} average precision (MAP) and \emph{mean} reciprocal rank
(MRR), averaged over all of the queries in the test set.  We also
report a weighted version of MAP, where the AP of each query is scaled
by the number of annotated correct answers to the query (shown as
W-MAP in the tables for space considerations).

@@

We next show the improvement gained by using the simple candidate
entity generation outlined in \secref{better-candidates}.  By simply
appending the list of connected entities in Freebase to the end of the
rankings returned by the distributional model, MAP improves by 40\%
(see \tabref{better-candidates}).  The connectedness of an entity pair
in Freebase is very informative, especially for rare entities that are
not seen together during training.

@@

\tabref{dev-results} shows a comparison between the semantic parsing
models we have discussed on the development set.  As can be seen, the
combined model significantly improves performance over prior work,
giving a relative gain in weighted MAP of 29\%.

@@

\tabref{final-results} shows that these improvements are consistent on
the final test set, as well.  The performance improvement seen by the
combined model is actually larger on this set, with gains on our
metrics ranging from 50\% to 87\%.

@@

Our model tends to outperform the distributional model on queries
containing predicates with exact or partial correlates in
Freebase. For example, our model obtains nearly perfect average
precision on the queries ``French newspaper \blank{}'' and ``Israeli
prime minister \blank{},'' both of which can be exactly expressed in
Freebase.  The top features for \lexicalpredicate{newspaper}($x$) all
indicate that $x$ has type \formalpredicate{newspaper} in Freebase,
and the top features for \lexicalpredicate{newspaper\_N/N}($x$, $y$)
indicate that $y$ is a newspaper, and that $x$ is either the
circulation area of $y$ or the language of $y$.

The model also performs well on queries with partial Freebase
correlates, such as ``Microsoft head honcho \blank{}'', ``The United
States, \blank{}'s closest ally'', and ``Patriots linebacker
\blank{},'' although with somewhat lower average precision. The high
weight features in these cases tend to provide useful hints, even
though there is no direct correlate; for example, the model learns
that ``honchos'' are people, and that they tend to be CEOs and film
producers.

@@

Second, our work is conceptually related to many methods that aim to
learn word embeddings that are informed by some kind of external
knowledge~\cite{faruqui-2015-retrofitting-word-vectors,%
rocktaschel-2015-logical-embeddings,schwartz-2016-symmetric-patterns-w2v,%
yu-2014-w2v-with-semantic-knowledge}.  A key difference between these
approaches and ours is that they use the structured information only
to modify distributional representations, while we include the
structured information directly in our models, training feature
weights jointly with distributional representations.

@@

This paper considers the problem of assigning meaning to predicates
(both categories and relations) in natural language using both
distributional information and information from a formal knowledge
base. Our model represents words as a weighted combination of
knowledge base queries plus a distributional component. Both of these
components are jointly trained to correctly predict entity answers to
fill-in-the-blank natural language queries. This combined model
achieved relative gains of over 50\% in mean average precision and
mean reciprocal rank versus a purely distributional approach.  We also
introduced a better mapping from surface text to logical forms, and a
simple method for using Freebase to find candidate entities during
inference.  Taken together, the methods introduced in this paper
improved mean average precision on our task from .163 to .370, a 127\%
relative improvement over prior work.
